---
title: "Project"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: united
---

```{r setup, include=FALSE, eval=T}
library(flexdashboard)
library(tidyverse)
library(sf)
library(spData)
library(ggplot2)
library(plotly)
library(leaflet)
library(readxl)
library(viridis)
library(patchwork)
library(hrbrthemes)
library(circlize)
library(chorddiag)  #devtools::install_github("mattflor/chorddiag")
library(wordcloud)
library(RColorBrewer)
```


About
=====================================
The project is aimed at analyzing and visualizing the spatial and temporal distribution of crime event in the city of Chicago in years 2018-2020. The project is expected to help people better understand the public safety issue in the city of Chicago and hopefully reduce the chance of crime events happening in the future.

The crime dataset used is part of the [Open Data Portal](https://data.cityofchicago.org/). It reflects reported incidents of crime (with the exception of murders where data exists for each victim) that occurred in the City of Chicago from 2001 to present. Data is extracted from the Chicago Police Department's CLEAR (Citizen Law Enforcement Analysis and Reporting) system. Variables in the dataset includes information about crime event type, location, time, if arrested, if domestic related, and so on.

The project use r language. The main package used includes: ggplot2, plotly, leaflet, wordcloud, tidyverse, chorddiag.


EDA {.storyboard}
=====================================

```{r, echo=F, eval=T}
# crime_2018 = read_csv("data/Crimes_-_2018.csv")
# crime_2019 = read_csv("data/Crimes_-_2019.csv")
# crime_2020 = read_csv("data/Crimes_-_2020.csv")
# 
# crime_extracted = rbind(crime_2018, crime_2019, crime_2020) %>%
#   select(Date, `Primary Type`, Description, `Location Description`, Arrest, Domestic, `Community Area`, Latitude, Longitude)
# 
# crime_major = crime_extracted %>% 
#   count(`Primary Type`) %>%
#   filter(n>1500) %>%
#   select(`Primary Type`) %>%
#   unique()
# 
# crime_extracted = crime_extracted[crime_extracted$`Primary Type` %in% crime_major$`Primary Type`,]
# 
# write.csv(crime_extracted, "data/crime_extracted.csv", row.names = F)


crime_all = read_csv("data/crime_extracted.csv", col_types = cols(Date=col_datetime(format = "%m/%d/%Y %H:%M:%S %p"),
                                                                  `Primary Type` = col_factor(),
                                                                  Description = col_character(),
                                                                  `Location Description` = col_character(),
                                                                  Arrest = col_logical(),
                                                                  Domestic = col_logical(),
                                                                  `Community Area` = col_integer(),
                                                                  Latitude = col_double(),
                                                                  Longitude = col_double()))
crime_all[crime_all$`Primary Type`=='CRIM SEXUAL ASSAULT', 'Primary Type'] = 'CRIMINAL SEXUAL ASSAULT'

crime_major = crime_all %>%
  select(`Primary Type`) %>%
  unique()


community_areas = st_read("data/geo_export_84bed4de-fc44-4a35-aa79-58fea2c4cc65.shp", quiet=T)

# trans_raw = read_csv('data/trans_2020.csv', col_types = cols(`Trip Start Timestamp`=col_datetime(format = "%m/%d/%Y %H:%M:%S %p"),
#                                                              `Trip End Timestamp`=col_datetime(format = "%m/%d/%Y %H:%M:%S %p"),
#                                                              `Pickup Community Area`=col_integer(),
#                                                              `Dropoff Community Area`=col_integer()))
# trans = trans_raw %>% 
#   select(`Trip Start Timestamp`, `Trip End Timestamp`, `Pickup Community Area`, `Dropoff Community Area`) %>%
#   filter(format(`Trip Start Timestamp`, '%Y-%m-%d')  <= "2020-01-07")
# 
# write.csv(trans, "data/trans.csv", row.names = F)

trans = read_csv("data/trans.csv")

```


### Crime Dataset Overview

```{r , eval=T}
knitr::kable(head(crime_all, n=30), caption = 'Crime Dataset Overview', align="c")
```
***

The table shows a few lines of the crime data. The whole dataset contains spatial-temporal information of recorded crime events since 2018.

### Transportation Dataset Overview

```{r , eval=T}
knitr::kable(head(trans, n=30), caption = 'Transportation Dataset Overview', align="c")
```
***

The table shows a few lines of the Transportation dataset. The dataset contains spatial-temporal information of recorded transportation trip in a week in Jan 2020.


### Primary Crime Type

```{r , eval=T}
crime_all %>% 
  count(`Primary Type`, Arrest) %>% 
  pivot_wider(names_from = `Arrest`, values_from=n) %>%
  mutate(`Total Number`=`FALSE`+`TRUE`,
         `Arrest Made`=`TRUE`,
         `Arrest not Made`=`FALSE`,
         `Percantage Arrested`=`Arrest Made`/`Total Number`) %>%
  # factor(data$Animals, levels = unique(data$Animals)[order(data$Count, decreasing = TRUE)])
  mutate(`Primary Type`= factor(`Primary Type`, levels=unique(`Primary Type`)[order(`Total Number`, 
                                                                                    decreasing = TRUE)])) %>%
  arrange(`Total Number`) -> crime_by_type
  
text_arr = paste("Percantage Arrested:", crime_by_type$`Percantage Arrested`*100) 

crime_by_type %>%
    plot_ly(
      x = ~`Primary Type`,
      y = ~`Arrest not Made`,
      type = "bar",
      name = "Not Arrested"
    ) %>% 
    
    add_trace(y=~`Arrest Made`,
              name="Arrested",
              text=text_arr) %>%
    
  
  layout(title = "Number of Recorded Crime Events by Primary Type Since 2018",
         xaxis = list(title = "",
                      tickangle = 45,
                      tickfont = list(
                          family = "Arial, sans-serif",
                          size = 10
                        ),
                      exponentformat = "E"),
         yaxis = list(title = "Number of Events"),
         barmode = 'stack')

```

***

The bar plot shows the crime primary type distribution. Notice that for many crime types, arrested cases took small part. The hover texts show the percentage of arrested cases for each category.

### Number of Crime Event in Each Month

```{r, eval=T}


crime_all %>% 
  select(Date) %>% 
  mutate(month = format(Date, "%Y-%m")) %>% 
  filter(month < '2020-12') %>% 
  count(month)-> crime_by_month


plot_ly(data=crime_by_month, 
        x = ~month,
        y = ~n,
        type='scatter',
        mode='lines') %>%
  layout(title = "Trend of Number of Crime Events of all Type over Time",
         xaxis = list(title = ""),
         yaxis = list(title = "Monthly Count of Crime Events") ) -> p

# for (ct in crime_major$`Primary Type`) {
#   p <-
#     p %>% plotly::add_trace(
#                             # x = crime_by_month$month,
#                             y = as.formula(paste0("~`", ct, "`")),
#                             name = ct,
#                             type='scatter',
#                             mode='lines'
#                 )
# }
p
```

***

Number of Crime Event in Each Month. There were less crime events happened in winter. There was a drop in 2020 due to COVID19 probably.

### Domestic Crime Percantage for each Crime type

```{r, fig.width=36,fig.height=18, eval=T}

crime_all %>%
  count(`Primary Type`, Domestic) %>%
  group_by(`Primary Type`) %>%
  mutate(perc = 100*n/sum(n),
         perc_dom = if_else(Domestic, perc, 0),
         perc_dom = max(perc_dom)) -> crime_dom
  
dom_levels = unique(crime_dom$`Primary Type`)[order(-unique(crime_dom$`perc_dom`))]

crime_dom %>%
  ungroup() %>%
  mutate(`Primary Type`= factor(`Primary Type`, levels=dom_levels)) -> d

  ggplot(d) +
    geom_bar(aes(x="", y=perc, fill=Domestic), 
             stat="identity",
             width=2) +
    coord_polar("y") +
    facet_wrap(~`Primary Type`, nrow=3) +
  theme_bw() +
  labs(x="",
       y="",
       title = 'Percantage of Domestic Related Crime by Different Crime Type') +
  theme(
        strip.text = element_text(size = 20),
        legend.text = element_text( size = 20),
        legend.title = element_text(size = 20),
        plot.title =  element_text(size = 20)
        )

```

***

This group of bar chart shows in order the percentage of domestics related crime by different crime type. As we can see domestic crime took significant percentage for many violent crimes types like batter, assault ans even sex offense. People should aware that those who are close to them can do harm to them.


Chicago Map Overview {data-navmenu="Spatial Analysis"}
==========================================================================

This is the map of the city of Chicago. Community Areas are small areas that compose the city of Chicago. This is the way we divide the city into smalls ares in this project.

Column
----------------------------------------------------

### Community Areas on Map

```{r, eval=T}
leaflet(data = community_areas) %>%
  addTiles() %>%
  addPolygons(label = ~community,
              color = "#444444",
              weight = 1,
              smoothFactor = 0.5,
              opacity = 1.0,
              fillOpacity = 0.5,
              highlightOptions = highlightOptions(color = "white",
                                                  weight = 2,
                                                  bringToFront = TRUE))
```


Column
----------------------------------------------------
### Community Area Numbers {data-commentary-width=400}

```{r, eval=T}
# crime_all %>% filter(`Primary Type`=="ROBBERY", !is.na(Longitude)) %>% 
#   st_as_sf(coords=c("Longitude", "Latitude"), crs=4326) -> rob_geom

community_areas %>% ggplot() +
  geom_sf(aes(geometry=geometry)) +
  geom_sf_text(aes(geometry=geometry,
                   label=area_num_1),
                size=2) +
  theme_bw() +
    labs(x="Longitude",
         y="Latitude",
         title="Chicago Commmunity Area")

```


Crime by Areas {data-navmenu="Spatial Analysis"}
==========================================================================

Column 
----------------------------------------------------

### Areas with Most Crime Events

```{r, eval=T}
number_crimes = crime_all %>% count(`Community Area`)

areas_crimes_num <- community_areas %>%
   select(community, area_numbe) %>%
   mutate(area_numbe = as.numeric(as.character(area_numbe))) %>%
   left_join(number_crimes,
             by = c("area_numbe" = "Community Area")) %>%
   mutate(n = ifelse(is.na(n), 0, n))

as.data.frame(areas_crimes_num) %>% 
  mutate(`Community Name`=community,
         `Area Numeber`=area_numbe,
         `Number of Events Since 2018`=n) %>%
  select(`Community Name`,
         `Area Numeber`,
         `Number of Events Since 2018`) %>%
  arrange(-`Number of Events Since 2018`) %>%
knitr::kable(align="c")
```

### Areas with Least Crime Events
```{r, eval=T}
as.data.frame(areas_crimes_num) %>% 
  mutate(`Community Name`=community,
         `Area Numeber`=area_numbe,
         `Number of Events Since 2018`=n) %>%
  select(`Community Name`,
         `Area Numeber`,
         `Number of Events Since 2018`) %>%
  arrange(`Number of Events Since 2018`) %>%
knitr::kable(align="c")
```

Column 
----------------------------------------------------

### Total Number of Reported Crime Events Since 2018 in Each Area

```{r, warning=F, eval=T}
bins <- c(0, 5000, 10000, 15000, 20000, 25000, Inf)
pal <- colorBin("RdYlBu", domain = areas_crimes_num$n, bins = bins, reverse = T)

areas_crimes_num %>%
  mutate(info = str_c("<strong>", community, "</strong>", "<br/>",
                      "Area Number: ", area_numbe, "<br/>",
                      "Total Number of Reported Crime Events Since 2018: ", n)
         %>%  map(htmltools::HTML)
         ) %>%
  leaflet() %>%
  addTiles() %>%
  addPolygons(label = ~info,
              fillColor = ~pal(n),
              color = "#444444",
              weight = 1,
              smoothFactor = 0.5,
              opacity = 1.0,
              fillOpacity = 0.5,
              highlightOptions = highlightOptions(color = "white",
                                                  weight = 2,
                                                  bringToFront = TRUE),
              labelOptions = labelOptions(
                style = list("font-weight" = "normal", padding = "3px 8px"),
                textsize = "10px",
                direction = "auto")) %>%
  addLegend(pal = pal,
            values = ~n,
            opacity = 0.7,
            title = NULL,
            position = "bottomright")
```

Property Crime {data-navmenu="Spatial-Temporal Analysis"}
==========================================================================

Number of theft events dropped since COVID19, however, number of burglary events raised during this time.

Community areas with most property crimes were NEAR NORTH SIDE, LOOP and NEAR WEST SIDE, which were close to each other.

There were more property crime during daytime.

Column
------------------------------

```{r, eval=T}
property_crime = c('THEFT', 'DECEPTIVE PRACTICE', 'BURGLARY', 'MOTOR VEHICLE THEFT')
violent_nsexual = c('BATTERY', 'ASSAULT', 'ROBBERY')
violent_sexual = c('SEX OFFENSE', 'CRIMINAL SEXUAL ASSAULT')
violent_public = c('CRIMINAL DAMAGE', 'WEAPONS VIOLATION', 
                   'CRIMINAL TRESPASS', 'PUBLIC PEACE VIOLATION')
homicide = c('HOMICIDE')

categorize = function(crime_type){
  if(crime_type %in% property_crime){
    'Property Crime'
  }else if(crime_type %in% violent_nsexual){
    'Violent Non Sexual'
  }else if(crime_type %in% violent_sexual){
    'Violent Sexual'
  }else if(crime_type %in% violent_public){
    'Violent Public'
  }else if(crime_type %in% homicide){
    'Homicide'
  }else{
    "Others"
  }
}

crime_all = crime_all %>% 
  mutate(Category=sapply(`Primary Type`, categorize))
```

```{r, eval=T}
plot_trend = function(crime_category){
  crime_all %>%
  filter(`Primary Type` %in% crime_category) %>%
  select(Date, `Primary Type`) %>% 
  mutate(month = format(Date, "%Y-%m")) %>% 
  filter(month < '2020-12') %>% 
  count(month, `Primary Type`) %>%
  pivot_wider(names_from = `Primary Type`, values_from=n) -> crime_by_month

  plot_ly(data=crime_by_month, x=~month) %>%
    layout(title = paste(crime_category, "Trend Over Time"),
           xaxis = list(title = ""),
           yaxis = list(title = "Monthly Count of Different Crime Types") ) -> p
  
  for (ct in crime_category) {
    p <-
      p %>% plotly::add_trace(
                              y = as.formula(paste0("~`", ct, "`")),
                              name = ct,
                              type='scatter',
                              mode='lines'
                  )
  }
  p
}

show_table = function(category){
  

   as.data.frame(community_areas) %>%
   select(community, area_numbe) %>%
   mutate(area_numbe = as.numeric(as.character(area_numbe))) %>%
   left_join((crime_all %>% 
              filter(Category == category) %>%
              count(`Community Area`)),
             by = c("area_numbe" = "Community Area")) %>%
   mutate(`Number of Events` = ifelse(is.na(n), 0, n),
          `Area Number` = area_numbe,
          `Community Name` = community) %>%
  select(`Community Name`, `Area Number`, `Number of Events`) %>%
  arrange(-`Number of Events`) %>%
  knitr::kable(align="c")
  
}

plot_heatmap = function(category, radius_tuning=5){
  crime_all %>%
  filter(Category==category) %>%
  mutate(time = format(Date, "%H:00")) %>%
  select(Latitude, Longitude, time) %>%
  drop_na() %>%

  plot_ly() %>%
    add_trace(
      type = 'densitymapbox',
      lat = ~Latitude,
      lon = ~Longitude,
      frame = ~time,
      colorscale="Viridis",
      radius = radius_tuning,
      showscale = FALSE
      ) %>%
    layout(
      mapbox = list(
        style='open-street-map',
        center= list(lon = -87.618994,
                     lat = 41.85),
        zoom=10
        ),
      coloraxis = list(coloraxis = list(colorscale = "Viridis"))
    )
}



```

### Number of Property Crime Events in Each Month

```{r, eval=T}
plot_trend(property_crime)
```


### Areas with Most Property Crimes

```{r, eval=T}
category = 'Property Crime'
show_table(category)
```


Column
------------------------------

### Property Crime Events Daily Heatmap

```{r, eval=T}

plot_heatmap(category, 4)

```



Violent Non-Sexual {data-navmenu="Spatial-Temporal Analysis"}
==========================================================================

Number of non-sexual violent crime events dropped in April 2020, then bounced back very quickly.

Community areas with most property crimes were AUSTIN and south area of Chicago.

Less non-sexual violent crime happened from 3 AM to 7AM.

Column
------------------------------

### Number of Non-Sexual Violent Crime Events in Each Month

```{r, eval=T}
plot_trend(violent_nsexual)
```


### Areas with Most Non-Sexual Violent Crimes

```{r, eval=T}
category = 'Violent Non Sexual'
show_table(category)
```


Column
------------------------------

###  Non-Sexual Crime Events Daily Heatmap

```{r, eval=T}
plot_heatmap(category)
```




Violent Sexual {data-navmenu="Spatial-Temporal Analysis"}
==========================================================================

Number of sexual violent crime events dropped in April 2020, then bounced back very quickly as well.

Community areas with most property crimes were AUSTIN and NEAR NORTH SIDE.

Column
------------------------------

### Number of Sexual Violent Crime Events in Each Month

```{r, eval=T}
plot_trend(violent_sexual)
```


### Areas with Most Sexual Violent Crimes

```{r, eval=T}
category = 'Violent Sexual'
show_table(category)
```


Column
------------------------------

###  Sexual Violent Crime Events Daily Heatmap

```{r, eval=T}
plot_heatmap(category, 8)
```



Violent Public {data-navmenu="Spatial-Temporal Analysis"}
==========================================================================
Number of public violent crime events dropped in April 2020, then bounced back.

Like non-sexual violent, community areas with most property crimes were AUSTIN and south area of Chicago.

Public violent crimes happened more frequently afternoon in a day.

Column
------------------------------

### Number of Public Violent Crime Event in Each Month

```{r, eval=T}
plot_trend(violent_public)
```


### Areas with Most Public Violent Crime

```{r, eval=T}
category = 'Violent Public'
show_table(category)
```


Column
------------------------------

###  Public Violent Crime Event Daily Heatmap

```{r, eval=T}
plot_heatmap(category)
```




Homicide {data-navmenu="Spatial-Temporal Analysis"}
==========================================================================

Number of homicide events increased significantly after March 2020.

Austin was still the area with most homicide crime events.

Column
------------------------------

### Number of Homicide Crime Events in Each Month

```{r, eval=T}
plot_trend(homicide)
```


### Areas with Most Homicide Crimes

```{r, eval=T}
category = 'Homicide'
show_table(category)
```


Column
------------------------------

### Homicide Crime Events Daily Heatmap

```{r, eval=T}
plot_heatmap(category)
```



Property Crime {data-navmenu="Text Analysis"}
==========================================================================


```{r, eval=T}
library(wordcloud)

drop_words = c("AND", "TO")


plot_wordcloud = function(category){
  tail(crime_all, 200000) %>%
  filter(Category==category) %>%
  select(Description) %>% 
  pull(Description) %>%
  paste(collapse = " ", sep = " ") %>%
  strsplit(" ") -> word_all
  
  word_all[!(word_all %in% drop_words)]  %>%
  table() -> word_freq

  wordcloud(names(word_freq), 
            as.integer(word_freq), 
            max.words = 200,
            random.color=T,
            colors=brewer.pal(8,"Dark2"),
            rot.per=.15)
}

plot_wordcloud_location = function(category){
  tail(crime_all, 200000) %>%
  filter(Category==category) %>%
  select(`Location Description`) %>% 
  pull(`Location Description`) %>%
  paste(collapse = " ", sep = " ") %>%
  strsplit(" ") %>%
  table() -> word_freq

  wordcloud(names(word_freq), 
            as.integer(word_freq), 
            max.words = 200,
            colors=brewer.pal(8,"Dark2"),
            rot.per=.15)
}

# get_word_freq = function(category, des_type='description'){
#     category = "Property Crime"
#     des_type='description'
#     des_type = if_else(des_type=='description', 'Description', 'Location Description')
#     tail(crime_all, 200000) %>%
#     filter(Category==category) %>%
#     select(des_type) %>% 
#     pull(des_type) %>%
#     paste(collapse = " ", sep = " ") %>%
#     strsplit(" ") -> word_all
#     
#     word_all[!(word_all %in% drop_words)]  %>%
#     table() -> word_freq
# }
# 
# get_word_freq("Property Crime")
```

Column {.tabset}
------------------------------

### Property Crime Description Word Cloud
```{r}
plot_wordcloud("Property Crime")
```


### Property Crime Location Description Word Cloud
```{r}
plot_wordcloud_location("Property Crime")
```


Column {data-width=150}
------------------------------

### Comment 
It seems that most property crimes involved less than $500 and mostly happened in apartments and stores.

<!-- ### Description Word Frequency -->

<!-- ```{r} -->
<!-- category = "Property Crime" -->
<!-- get_word_freq(category, 'description') %>% -->
<!--   knitr::kable(align="c") -->
<!-- ``` -->

<!-- ### Locaiton Word Frequency -->

<!-- ```{r} -->
<!-- get_word_freq(category, 'location') %>% -->
<!--   knitr::kable(align="c") -->
<!-- ``` -->

Violent Non Sexual Crime {data-navmenu="Text Analysis"}
==========================================================================

Column {.tabset}
------------------------------

### Non-Sexual Violent Crime Description Word Cloud
```{r, eval=T}
plot_wordcloud("Violent Non Sexual")
```

### Non-Sexual Violent Crime Location Description Word Cloud
```{r}
plot_wordcloud_location("Violent Non Sexual")
```

Column {data-width=150}
------------------------------

### Comment
Many non-sexual crimes were domestic. Most of these type of crime happened on street and in store. 

<!-- ### Description Word Frequency -->

<!-- ```{r} -->
<!-- category = "Violent Non Sexual" -->
<!-- get_word_freq(category, 'description') %>% -->
<!--   knitr::kable(align="c") -->
<!-- ``` -->

<!-- ### Locaiton Word Frequency -->

<!-- ```{r} -->
<!-- get_word_freq(category, 'location') %>% -->
<!--   knitr::kable(align="c") -->
<!-- ``` -->

Violent Sexual Crime {data-navmenu="Text Analysis"}
==========================================================================

Column {.tabset}
------------------------------

### Sexual Violent Crime Description Word Cloud
```{r, eval=T}
plot_wordcloud("Violent Sexual")

```

### Sexual Violent Crime Location Description Word Cloud
```{r}
plot_wordcloud_location("Violent Sexual")
```


Column {data-width=150}
------------------------------

### Comment
Many sexual crimes involved sexual abuse and non-consensual sex. This type of crime could happen in a wide range of places.

<!-- ### Description Word Frequency -->

<!-- ```{r} -->
<!-- category = "Violent Sexual" -->
<!-- get_word_freq(category, 'description') %>% -->
<!--   knitr::kable(align="c") -->
<!-- ``` -->

<!-- ### Locaiton Word Frequency -->

<!-- ```{r} -->
<!-- get_word_freq(category, 'location') %>% -->
<!--   knitr::kable(align="c") -->
<!-- ``` -->

Public Violent Crime {data-navmenu="Text Analysis"}
==========================================================================

Column {.tabset}
------------------------------

### Public Violent Crime Description Word Cloud
```{r, eval=T}
plot_wordcloud("Violent Public")
```

### Public Violent Crime Location Description Word Cloud
```{r}
plot_wordcloud_location("Violent Public")
```

Column {data-width=150}
------------------------------

### Comment
Many public violence involved property damage and vehicle damage. Mostly happened on street.

<!-- ### Description Word Frequency -->

<!-- ```{r} -->
<!-- category = "Violent Public" -->
<!-- get_word_freq(category, 'description') %>% -->
<!--   knitr::kable(align="c") -->
<!-- ``` -->

<!-- ### Locaiton Word Frequency -->

<!-- ```{r} -->
<!-- get_word_freq(category, 'location') %>% -->
<!--   knitr::kable(align="c") -->
<!-- ``` -->

Network Analysis
==========================================================================

Column
------------------------------

### Transportation Between Different Community Areas

```{r, fig.height=20, fig.width=20, eval=T}
trans %>% 
  count(`Pickup Community Area`, `Dropoff Community Area`) %>%
  mutate(from=as.character(`Pickup Community Area`),
         to=as.character(`Dropoff Community Area`),
         value=n) %>%
  select(from, to, value) %>%
  drop_na() %>%
  filter(value > 500) -> trans_network

# color palette
set.seed(2333)
nsections = length(unique(trans_network$to))
mycolor <- viridis(nsections, alpha = 1, begin = 0, end = 1, option = "D")
mycolor <- mycolor[sample(1:nsections)]
chordDiagram(trans_network, 
             annotationTrack = "grid",
             grid.col = mycolor,
             preAllocateTracks = list(track.height = max(strwidth(unlist(dimnames(trans_network))))),
             transparency = 0.25,
              directional = 1,
              direction.type = c("arrows", "diffHeight"), 
              diffHeight  = -0.04,
              annotationTrackHeight = c(0.05, 0.1),
              link.arr.type = "big.arrow", 
              link.sort = TRUE, 
              link.largest.ontop = TRUE)
# Add text
circos.track(track.index = 1,
             bg.border = NA,
             panel.fun = function(x, y) {
               
                  circos.text(CELL_META$xcenter, 
                              CELL_META$ylim[1], 
                              CELL_META$sector.index, 
                              facing = "clockwise", 
                              niceFacing = TRUE,  
                              adj = c(0, 0.8),
                              cex=1)
                   # Add graduation on axis
             }
             
             )
title(main=list("Transportation Between Different Community Areas", 
                cex = 2))
```

Column
------------------------------

### Areas with Highest Number of Crime

```{r, eval=T}
crime_all %>%
  count(`Community Area`) %>%
  mutate(`Number of Crime`=n) %>%
  select(`Community Area`, `Number of Crime`) %>%
  arrange(-`Number of Crime`) %>%
  head(30) %>%
  knitr::kable(caption = paste('Areas with Highest Number of Crime Events'),  align="c")
```

### Comment

The network shows the number of transportation reported by Transportation Network Providers. Areas 8, 32 and 28 had busy transportation and considerably high crime rate. Government should consider reinforce police force in these areas.
